### 2019-04-02 2_metg.tex
Small tweaks to make text fit better.

Figures~\ref{fig:flops-mpi} and \ref{fig:efficiency-mpi} show how METG is
calculated. The application, in this case an MPI implementation of the
Task Bench stencil pattern in Figure~\ref{fig:task-graphs-stencil}, is
run on a single Haswell node of Cori with a problem size large enough to
ensure that it achieves peak FLOPS. This starting point confirms
that the application is properly configured and that the choice of
efficiency metric is achievable. The problem
size is then repeatedly reduced while maintaining exactly the same hardware
configuration (in particular, the same number of nodes). The
expectation is that as problem size shrinks,
performance will begin to drop and eventually approach zero, as shown in Figure~\ref{fig:flops-mpi}. Systems
with lower runtime overheads maintain higher performance at smaller
problem sizes compared to systems with higher overheads.

To calculate METG, the data is replotted along axes of efficiency
(i.e., as a percentage of the peak FLOPS achieved) and task
granularity (i.e., $\text{wall time} \times \text{number of
  cores}/\text{number of tasks}$), as shown in Figure~\ref{fig:efficiency-mpi}. Note that a \emph{task} is defined
broadly to be any continuously-executing unit of application code,
and thus it makes sense to discuss tasks even in systems
without an explicit notion of tasking, such as in MPI programs that
are written in a bulk synchronous style. In this case, the tasks run a
compute-bound kernel included in the Task Bench implementation,
described in more detail in Section~\ref{sec:task-bench}.

>>>>

Figures~\ref{fig:flops-mpi} and \ref{fig:efficiency-mpi} show how METG is
calculated. The application, in this case an MPI implementation of the
Task Bench stencil pattern in Figure~\ref{fig:task-graphs-stencil}, is
run on a single Haswell node of Cori~\cite{Cori} with a problem size large enough to
ensure that it achieves peak FLOPS. This confirms
that the application is properly configured and that the
efficiency metric is achievable. The problem
size is then repeatedly reduced while maintaining exactly the same hardware
configuration (in particular, the same number of nodes). The
expectation is that as problem size shrinks,
performance will begin to drop and eventually approach zero, as shown in Figure~\ref{fig:flops-mpi}. Systems
with lower runtime overheads maintain higher performance at smaller
problem sizes compared to systems with higher overheads.

To calculate METG, the data is replotted along axes of efficiency
(i.e., as a percentage of the peak FLOPS achieved) and task
granularity (i.e., $\text{wall time} \times \text{number of
  cores}/\text{number of tasks}$), as shown in Figure~\ref{fig:efficiency-mpi}. Note that a \emph{task} is defined
broadly to be any continuously-executing unit of application code,
and thus it makes sense to discuss tasks even in systems
without an explicit notion of tasking, such as in MPI programs written in a bulk synchronous style. In this case, the tasks run a
compute-bound kernel included in the Task Bench implementation,
described in more detail in Section~\ref{sec:task-bench}.

### 2019-04-02 3_task_bench.tex
Small tweaks to make text fit better.

For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, column $i$ represents all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column of the task graph will be
assigned to execute on a different processor core.

Dependencies between tasks are controlled by a configurable dependence
relation. The
dependence relation enumerates, for each task, the set of tasks in the
previous time step that task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, and so on. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

>>>>

For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, column $i$ represents all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column will be
assigned to execute on a different processor core.

Dependencies between tasks are controlled by a configurable dependence
relation. The
dependence relation enumerates the set of tasks from the
previous time step each task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, etc. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

### 2019-04-02 4_implementation.tex
Small tweaks to make text fit better.

OmpSs~\cite{OmpSs11} is a programming model for loop- and task-based parallelism
that is source-compatible with OpenMP. Our Task Bench implementation
uses OpenMP 4.0-style tasks with task dependencies. Because tasks in
OpenMP 4.0 have a fixed number of dependencies, we use a switch
statement to implement the dynamic dependencies required for Task
Bench. The implementation is otherwise straightforward.

@@

OpenMP~\cite{OpenMPSpec40} is the industry standard API for loop-based
parallelism on shared-memory systems, and supports task dependencies as of version 4.0. Our Task Bench implementation
for OpenMP is very similar to OmpSs and uses tasks with
task dependencies.

In our evaluation, we test with both GNU GOMP and Intel KMP
implementations of OpenMP. We found KMP to provide better performance
and report KMP numbers in our evaluation.

>>>>

OmpSs~\cite{OmpSs11} is a programming model for loop- and task-based parallelism
that is source-compatible with OpenMP. Our Task Bench implementation
uses OpenMP 4.0-style task dependencies. Because OpenMP tasks have a fixed number of dependencies, we use a switch
statement to implement the dynamic dependencies required for Task
Bench. The implementation is otherwise straightforward.

@@

OpenMP~\cite{OpenMPSpec40} is the industry standard API for loop-based
parallelism on shared-memory systems, and supports task dependencies as of version 4.0. Our Task Bench implementation
for OpenMP is very similar to OmpSs and uses tasks with
task dependencies. We tested both GNU GOMP and Intel KMP
implementations of OpenMP and found KMP to be better performing.
